\chapter*{Glossary}
\addcontentsline{toc}{chapter}{Glossary}
\markboth{GLOSSARY}{}

% TODO: (aver) Ask Eryk if good as is
%	        https://csrc.nist.gov/glossary
%	        do i need to define these things in text or just here?

\begin{description}
	\item [Attestation] It is the claim by one entity over another, e.g, the driver license is an attestation by the
	      Motor Vehicle Department (US), that one may drive a car. \cite{eth-decentralized-identity}
	\item [Authentication] Verifying the identity of a user, process, or device, often as a prerequisite to
	      allowing access to resources in an information system. \cite{nist:glossary}
	\item [Accounting] Access privileges granted to a user, program, or process or the act of granting those
	      privileges. \cite{nist:glossary}
	      % TODO: (aver) Add citation
	\item [Authorization] Authorization is the decision whether an entity is allowed to perform a particular action
	      or not, e.g., whether a user is allowed to attach to a network or not.
	\item [Cloud Computing] Cloud computing is the on-demand availability of computer system resources, especially
	      data storage and computing power, without direct active management by the user. \cite{nist:glossary}
	\item [Edge Computing] Edge computing is the placement of storage and computing resources closer to source, where
	      the data is generated. \cite{nist:glossary}
	\item [Firmware] Computer programs and data stored in hardware - typically in read-only memory (ROM) or
	      programmable read-only memory (PROM) - such that the programs and data cannot be dynamically written
	      or modified during execution of the programs. \cite{nist:glossary}
	\item [IoT] Internet of Things refers to an interconnected infrastructure, featuring objects, people, systems and
	      information resources, where with intelligent services the processing of physical information and the
	      virtual world can react. \cite{iot-guide-definition}
	\item [Line-Replaceable Unit] modular component of airplane, designed to be replaced quickly
	\item [Fog Computing] As an extension of Cloud computing, Fog Computing brings the computation closer to IoT
	      Edge devices. \cite{nist:glossary}
	\item [Manufacturer Usage Description] A component-based architecture specified in Request for Comments (RFC)
	      8520 that is designed to provide a means for end devices to signal to the network what sort of access and
	      network functionality they require to properly function. \cite{nist:glossary}
	\item [Self-Sovereign Identity] Defined as a portable digital ID that exists throughout the lifetime of a device
	      and does not depending on a central authority. \cite {w3c2022did}
	      % TODO: (aver) Add citation
	\item [Trust Model] In the trust model the issuer issues credential to a holder while the holder can prove
	      identity by showing the credential to a verifier.
	\item [Trusted Execution Zone] An area or enclave protected by a system processor. \cite{nist:glossary}
\end{description}
